Blockchain System

### 2020-10-12 papers/execution-model/model.tex
revising rules

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}

@@

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a pending operation). 
 \begin{definition}[Pending operation]
A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}[Accepted operation]
An accepted operation  is a tuple $\langle  \OP, \OPH, \TIME \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash and
$\TIME$ is the time when it was included in the blockchain. 
\end{definition}

\begin{definition}[Blockchain]
  The state of a blockchain is a tuple
  $[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a set of pending operations,  $\ACCEPTED$ is a set
  of accepted operations, $\MANAGERS$ is a set of managers,
  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time of the blockchain. 
\end{definition}

\begin{definition}[Blockchain system]
A blockchain system is a pair
$ \NODE \| \BLOCKCHAIN$ where
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.pkh = c.pkh$
  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.puh = p.puh$.
\end{enumerate}
\end{definition}

@@

Rule 1 [proposal]:

\begin{equation}{}
  \frac{
    \text{checkAcc($pkh$, \ACCOUNTS)}
  }{
    \parbox{4.5in}{\text{$\langle[\ACCOUNTS, \OPERATIONS,
        \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
        \TIME]\rangle \rightarrow$} \\
      \text{$\langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ)$ ::
        \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
        \CONTRACTORS, \TIME]$\rangle$}}}  
\end{equation}
~\\
~\\
Rule 2 [injected]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{equation}{}
\frac{}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$ } \\
 \text{[\PENDING, $<$ transfer $n$ from  $puk$ to $puk'$ fee $m$, oph, \TIME' $>$ :: \ACCEPTED, updateSucc(\MANAGERS, } \\
\text{$puk, puk', n, m$), \CONTRACTORS, \TIME' + 1]}}} 
\end{equation}
~\\
Rule 7 [timeout]:
\begin{equation}{}
\frac{\TIME' - \TIME \ge 60}{\parbox{4.2in}{\text{[$<$ transfer $n$ from $puk$ to  $puk'$ fee $m$, oph, \TIME $>$ :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME' ] $\rightarrow$} \\
 \hspace*{0cm} \text{[\PENDING, \ACCEPTED, updateCou(\MANAGERS, $puk$, False), \CONTRACTORS, \TIME']}}} 
\end{equation}

\subsection{Smart Contracts}
~\\
A. Originate
~\\
~\\
Rule 1 [proposal]:

\begin{equation}{}
  \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
  {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
        [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
        \rightarrow \langle$[\ACCOUNTS, 
        (originate contract ${id}$ transferring} \\
  \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 2 [injected]:

\begin{equation}{}
\frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
\end{equation}
~\\
~\\
Rule 3 [rejected of code]:

>>>>

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}

@@

When an operation is injected in a node, it enters a \emph{pending pool}
(and is called a \emph{pending operation}). 
 \begin{definition}[Pending operation]
A pending operation is a tuple  $\langle  \OP, \OPH, \TIME
\rangle $, where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected. 
\end{definition}
After some time, a pending operation may be included in the blockchain as an accepted operation.
%Let \textit{P} is the set of pending operations.
 \begin{definition}[Accepted operation]
An accepted operation  is a tuple $\langle  \OP, \OPH, \TIME \rangle
$, where $\OP$ is an operation, $\OPH$ is the operation hash, and
$\TIME$ is the time when it was included in the blockchain. 
\end{definition}

\begin{definition}[Blockchain]
  The state of a blockchain is a tuple
  $[\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ where
  $\PENDING$ is a set of pending operations,  $\ACCEPTED$ is a set
  of accepted operations, $\MANAGERS$ is a set of managers,
  $\CONTRACTORS$ is a set of contractors, and $\TIME$ is the current time. 
\end{definition}

\begin{definition}[Blockchain system]
A blockchain system is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS, \CONTRACTS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$ is the state of a blockchain 
  such that $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PKH = c.\PKH$
  and $\forall s \in \CONTRACTS \implies \exists p \in \CONTRACTORS, s.\PUH = p.\PUH$.
\end{enumerate}
\end{definition}

@@

% Rule 1 [proposal]:
%
% \begin{mathpar}
%   \inferrule[Xfer-Propose]{
%     \CHECKACC (\PKH, \ACCOUNTS)
%   }{
% \langle[\ACCOUNTS, \OPERATIONS,
%         \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
%         \TIME]\rangle \rightarrow \\
%         \langle [\ACCOUNTS, (\TRANSFER\NTEZ\PKH{\PKH'}\MTEZ) ::
%         \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS,
%         \CONTRACTORS, \TIME]\rangle      }
% \end{mathpar}

Rule 2 [injected]:

@@

\begin{equation}{}
\frac{\text{$\neg$ checkPub(\MANAGERS, $pkh'$)}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (transfer $n$ from $pkh$ to $pkh'$ fee $m$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle \rightarrow$ }\\
\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
\end{equation}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    % \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']} \rightarrow 
    {[\PENDING, \Angle{\OP,\OPH,\TIME'} :: \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']} \rightarrow 
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

\subsection{Smart Contracts}
~\\
A. Originate
~\\
~\\
% Rule 1 [proposal]:

% \begin{equation}{}
%   \frac{\text{checkAcc($pkh$, \ACCOUNTS) $\wedge$ checkId($id$, \CONTRACTS)}}
%   {\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
%         [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle
%         \rightarrow \langle$[\ACCOUNTS, 
%         (originate contract ${id}$ transferring} \\
%   \text{${n}$ from ${pkh}$} \text{running ${code}$ init ${s}$) :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]$\rangle$}}} 
% \end{equation}
% ~\\
% ~\\
Rule 2 [injected]:

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \ORIG = \ORIGINATE\ID\NTEZ\PUK\CODE\STRING\MTEZ 
  }{
    \Angle{[
      \ACCOUNTS, \ORIG :: \OPERATIONS, \CONTRACTS
      ], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]} \to \\
    \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\ORIG :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]}
  }
\end{mathpar}
% \begin{equation}{}
% \frac{\text{checkBal(\MANAGERS, $pkh, n, m$) $\wedge$ checkCou(\MANAGERS, $pkh$) $\wedge$ \text{checkPrg($code, s$)}}}{\parbox{4.2in}{\text{$\langle$[\ACCOUNTS, (originate contract ${id}$ transferring  ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{ :: \OPERATIONS, \CONTRACTS], [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] $\rangle \rightarrow \langle$ [\ACCOUNTS, \OPERATIONS, \CONTRACTS],} \text{[(originate contract ${id}$ transferring ${n}$ from ${pkh}$ running ${code}$ init ${s}$)} \text{:: \PENDING, \ACCEPTED, updateCou(\MANAGERS, $pkh$, True), \CONTRACTORS, \TIME] $\rangle$}}} 
% \end{equation}
~\\
~\\
Rule 3 [rejected of code]:
